Type Refinements for the Working Class

### 2015-11-14 paper.tex
notation

Then, a \emph{lazy computation system} (lcs) is a lazy computation language
$\Match{L}{\Pair{\Sigma}{\CanOperators}}$ along with an indexed
$\alpha$-functional relation
$\Of{\Downarrow}{\Pow{\Exprs\times\Values\times\NaturalsPsh}}$ where
$\NaturalsPsh$ is the constant presheaf $\MapsTo{(\Upsilon, \tau)}{\Naturals}$.
We will write $\EvalN{\Upsilon}{\tau}{n}{M}{N}$ when
$\Member{\Tuple{M,N,n}}{\Downarrow_\tau(\Upsilon)}$, to mean that $M$ evaluates
to $N$ in $n$ steps.

>>>>

Then, a \emph{lazy computation system} (lcs) is a lazy computation language
$\Match{L}{\Pair{\Sigma}{\CanOperators}}$ along with an indexed
$\equiv_\alpha$-functional relation
$\Of{\Downarrow}{\Pow{\Exprs\times\Values\times\NaturalsPsh}}$ where
$\NaturalsPsh$ is the constant presheaf $\MapsTo{(\Upsilon, \tau)}{\Naturals}$.
We will write $\EvalN{\Upsilon}{\tau}{n}{M}{N}$ when
$\Member{\Tuple{M,N,n}}{\Downarrow_\tau(\Upsilon)}$, to mean that $M$ evaluates
to $N$ in $n$ steps.
